peter_models

### 2024-12-07 peter_models.qmd
updating olr models

# dataset_clean$Q271_reordered <- factor(dataset_clean$Q271,
#                             levels = c("(5) Not at all important",
#                                      "(4) Slightly important",
#                                      "(3) Moderately important",
#                                      "(2) Very important",
#                                      "(1) Extremely important"))

ord_mod_interactions <- polr(Q29 ~ Q271_reordered + race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            S3B + # Gender
            Q21, # Party affiliation
          data = dataset_clean, Hess=TRUE)

>>>>

ord_mod_interactions <- polr(Q29 ~ Q271_reordered + race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            S3B + # Gender
            Q21, # Party affiliation
            # Q271_reordered * race_recoded,  # Interaction term
          data = dataset_clean, Hess=TRUE)
